Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-19 fmics/paper.tex
Reword first two paragraphs of introduction.

The Large Hadron Collider (LHC) at the European Organization for Nuclear Research (CERN) provides a head-on collisions of protons at a center of a mass energy of 14 TeV for high energy particle physics research. %The LHC is installed in a 27 km long LEP tunnel. 
In order to reach the required magnetic field strengths, superconducting magnets cooled with superfluid helium are used. In addition to the energy stored in the LHC, the 700 MJ stored in the circulating beams could initiate quenches (transition of the superconductors to normal conducting state) and cause damages if only a very small fraction of the circulating beam particles deposit their energy in the equipment. The consequences of such event ranges from several hours of down time for cooling down the magnets to reach the superconducting state again, to months of repairs in the case of equipment damage.

The strategy for machine protection of the LHC is mainly based on the Beam Loss Monitoring (BLM) system. At each turn of the beam, BLM records several thousands of data and process them in order to decide to signal the safe extraction of the beam if losses exceed quench level thresholds. The processing involves a proper analysis of the loss pattern in time and the energy of the beam.

>>>>

The Large Hadron Collider (LHC) at the European Organization for Nuclear Research (CERN) is a high-energy particle accelerator.
It collides beams of protons, where each particle has an energy of 14 TeV, and the results of these collisions are used for high-energy physics research.
In order to reach the required magnetic field strengths, the LHC has superconducting magnets cooled with superfluid helium.
Because the energy of the beams is so high (700 MJ), if even a small fraction of the beam particles leak into the equipment they can cause the superconductors to transition to their normal conducting state.
Such a transition is called a quench.
The consequences of a quench range from several hours of down time (to cool the magnets back down to their superconducting state), to months of repairs (in the case of equipment damage).

The main strategy for protecting the LHC from quenches is the Beam Loss Monitoring (BLM) system, which stops the beams safely if the particle loss exceeds thresholds that are likely to result in a quench. 
At each cycle of the beams around the LHC, the BLM system records and processes thousands of data points in order to decide whether to stop the beams.
The processing includes analysis of the loss pattern over time and of the energy of the beam.
